Dependent Object Types

### 2012-09-07 doc/candidacy/slides.tex
confs

\begin{frame}{Selected Papers}
\begin{enumerate}
\item {\it A Type-Theoretic Approach to Higher-Order
  Modules with Sharing}\\{\footnotesize\textcolor{gray}{by Robert Harper and Mark
  Lillibridge}}\begin{itemize}
\item calculus for modules in the ML tradition
\item modules are first-class values
\end{itemize}
\item {\it Tribe: a simple virtual class calculus}\\
  {\footnotesize\textcolor{gray}{by Dave Clarke, Sophia Drossopoulou, James Noble and Tobias Wrigstad}}\begin{itemize}
\item calculus for virtual classes
\item paths are types, and types are ``generalized'' paths
\end{itemize}
\item {\it A Nominal Theory of Objects with Dependent
  Types}\\{\footnotesize\textcolor{gray}{by Martin Odersky, Vincent Cremet, Christine R{\"o}ckl and
  Matthias Zenger}}\begin{itemize}
\item calculus unifying advanced object-oriented and module systems
\item foundation for Scala
\end{itemize}
\end{enumerate}
\end{frame}

>>>>

\begin{frame}{Selected Papers}
\begin{enumerate}
\item {\it A Type-Theoretic Approach to Higher-Order
  Modules with Sharing}\\{\footnotesize\textcolor{gray}{by Robert Harper and Mark
  Lillibridge\\POPL '94}}\begin{itemize}
\item calculus for modules in the ML tradition
\item modules are first-class values
\end{itemize}
\item {\it Tribe: a simple virtual class calculus}\\
  {\footnotesize\textcolor{gray}{by Dave Clarke, Sophia Drossopoulou, James Noble and Tobias Wrigstad\\AOSD '07}}\begin{itemize}
\item calculus for virtual classes
\item paths are types, and types are ``generalized'' paths
\end{itemize}
\item {\it A Nominal Theory of Objects with Dependent
  Types}\\{\footnotesize\textcolor{gray}{by Martin Odersky, Vincent Cremet, Christine R{\"o}ckl and
  Matthias Zenger\\ECOOP '03}}\begin{itemize}
\item calculus unifying advanced object-oriented and module systems
\item foundation for Scala
\end{itemize}
\end{enumerate}
\end{frame}
